%-------------------------------------------------------------------------------
% LaTeX Resume Template
% Compile with: pdflatex resume.tex  (or use Overleaf)
%-------------------------------------------------------------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{tabularx}
\input{glyphtounicode}

%---------- Page & Margin Setup ----------
\usepackage[margin=0.5cm]{geometry}
\addtolength{\topmargin}{-0.5cm}
\addtolength{\textheight}{1.0cm}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%---------- Section Formatting ----------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine-readable / ATS-friendly
\pdfgentounicode=1

%---------- Custom Commands ----------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%===============================================================================
\begin{document}

%---------- HEADING ----------
\begin{center}
    {\LARGE \scshape \vspace{1pt} Sreeja Deb} \\ \vspace{1pt}
    \small
    \faPhone* \ +91-8349605201 \ $|$ \
    \href{mailto:srde@microsoft.com}{\faEnvelope \ srde@microsoft.com} \ $|$ \
    \href{https://www.linkedin.com/in/sreeja-deb-887192135/}{\faLinkedin \ linkedin.com/in/sreeja-deb-887192135}
\end{center}

%---------- SUMMARY ----------
\section{Summary}
\small{
AI Engineer with 7+ years of experience designing \& delivering end-to-end AI and
data platforms. Skilled across the full spectrum of AI, from traditional machine
learning (predictive modeling, AutoML, \& MLOps) to the latest generative \& agentic
AI (LLM-powered agents, RAG, \& Graph-RAG). Strong foundation in large-scale data
engineering, adept at taking solutions from data modeling \& experimentation to
scalable, secure production. Passionate about democratizing AI \& drive innovation.
}
\vspace{-4pt}

%---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Georgia Institute of Technology} -- M.S. Computer Science (Spec. ML/AI), GPA: 3.9/4.0}{2023 -- 2026}
  \resumeProjectHeading
    {\textbf{NIT Bhopal} -- B.Tech Computer Science \& Engineering, CGPA: 8.17/10}{2015 -- 2019}
  \resumeProjectHeading
    {\textbf{Kendriya Vidyalaya (CBSE)} -- Class 12\textsuperscript{th}: 95.4\%, Class 10\textsuperscript{th}: 98.6\%}{2004 -- 2015}

\resumeSubHeadingListEnd

%---------- EXPERIENCE ----------
\section{Experience}
\resumeSubHeadingListStart

  %-------- Microsoft --------
  \resumeSubheading
    {Microsoft}{India}
    {SDE2 (L62) - Data Engineering/ Data Science / Agentic AI}{2019 -- Present}
    \resumeItemListStart
      \resumeItem{\textbf{Account Researcher AI Agent Platform:} Architected a
        production LLM-powered agent converting natural-language sales queries into grounded
        insights, using a scalable FastAPI microservice. Engineered an agentic
        orchestration loop with query decomposition, parallel LLM calls and
        NL2SQL grounded via RAG over Azure AI Search, driving accuracy with iterative prompt
        tuning, semantic validation, \& self-correction against business rules. Optimized
        latency \& token cost via semantic caching, async concurrency, \& SQL connection
        pooling; hardened with row-level security, \& telemetry tracing.
        Deployed on Azure \& piloted to 3k+ sellers across Microsoft globally.}
      \resumeItem{\textbf{Customer Graph-RAG:} Built an end-to-end
        Graph-RAG platform transforming Microsoft's global enterprise customer data across
        multiple domains (Account, Opportunity, Customer Health, and Azure Consumed Revenue etc)
        into a unified knowledge graph that answers natural-language questions with grounded
        LLM responses and a live subgraph visualization for explainability. Architected a
        three-stage pipeline: offline graph build using Fabric Graph, in-memory load, and
        real-time serving via a semantic retrieval engine over Azure OpenAI embeddings.}
      \resumeItem{\textbf{AutoBrewML:} Created an
        open-source Microsoft framework that automates the end-to-end machine learning
        workflow (data prep, model training, \& deployment) on Azure, letting teams build
        models with 80\% less manual effort \& no prior ML expertise. Published on PyPI
        (\textasciitilde2{,}000 downloads in the first month), presented as lead speaker at
        Microsoft's internal Machine Learning, AI \& Data Science (MLADS) conference, and
        filed a patent for its data-sampling module, later reused by the Microsoft Cloud
        Data Science team to speed up incident debugging on smaller data samples.}
      \resumeItem{\textbf{MLOps / AIOps Platform:} Led the design \& build of a unified
        MLOps \& AIOps platform on Microsoft Fabric that gives teams a standardized, secure
        way to ship both classical ML models and LLM-powered agents end-to-end, automating
        model training, versioning, monitoring, deployment, data-drift detection, and
        retraining for classical ML while operationalizing generative \& agentic AI through
        prompt/version management, LLM evaluation and guardrails, RAG pipeline
        orchestration, and continuous quality, latency, cost, and hallucination telemetry.}
      \resumeItem{\textbf{Predictive Resource Forecasting:} Built a machine learning model
        that forecasts each consultant's weekly billable hours at 75--80\% accuracy,
        replacing a manual planning process for Project Managers (whose compensation is tied
        to planning accuracy); adopted globally after a successful pilot.}
      \resumeItem{\textbf{Automated Data Tagging:} Built a recommendation engine that
        automatically assigns business-friendly labels to newly ingested data columns
        across a large commercial data platform (Sales, Consumption, Marketing, Finance,
        \& Professional Services), using a hybrid approach combining keyword-frequency
        (TF-IDF) \& word-embedding techniques to save significant manual engineering effort.}
      \resumeItem{\textbf{Enterprise Data Warehousing \& BI:} Designed \& maintained multiple
        large-scale data warehouses \& ETL processes that consolidated data from multiple
        sources into a single 1M+ user platform, delivering business intelligence and
        reporting for a multi-million-dollar Microsoft Consulting Services solution.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%---------- LEADERSHIP & OUTREACH ----------
\section{Leadership \& Community Outreach}
\resumeSubHeadingListStart
  \item[]
  \resumeItemListStart
    \resumeItem{\textbf{Diversity \& Inclusion Lead, Microsoft India:} Drove diversity \& inclusion for the Digital
      Professional Services org in India, launching a sustainable, non-conventional
      program alongside senior leadership, HR, \& Legal. Improved D\&I scores in the
      company-wide employee sentiment (Pulse) survey, with the initiative featured in the
      India Development Center newsletter for its unique approach.}
    \resumeItem{Coordinated external outreach programs for underprivileged girls and
      women with the \textbf{Microsoft India Philanthropy} team \& the \textbf{Women@Microsoft External
      Outreach} pillar}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%---------- SKILLS ----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Focus Areas:} Machine Learning \& Modelling (MLOps), Generative / Agentic /
    NLP Solutions (AIOps), RAG \& Graph-RAG, Data Modelling, Database Development,
    Business Intelligence (BI), Azure Cloud Infrastructure \\ \vspace{2pt}
    \textbf{Languages \& Frameworks:} Python, SQL, Scala, PyTorch, TensorFlow, Scikit-learn, Pandas, Spark, PySpark \\ \vspace{2pt}
    \textbf{Platforms \& Tools:} Azure OpenAI, Azure AI Search, Azure Cognitive Services,
    Microsoft Fabric, Azure Data Factory, Azure Data Lake,
    Azure Synapse, Azure Databricks, Power BI
  }}
\end{itemize}

%===============================================================================
\end{document}
